### 2017-06-29 Plos-one-manuscript/latex/manuscript.tex
working on revision

Our solution was to replace the built-in scale with a scale that accounted for the expansion.
We compared expected volumes with actual measurements and noticed a linear relationship.
We scaled up the graduations by a factor of 1.027x for both the 100-1000 $\mu$L, and 30-300 $\mu$L configurations.
These scales were exported to portable document format (PDF) so that they are most easily printed to scale.
These adjusted scales are printed on a transparency sheet and taped onto the syringe with the zero at plunger in the latched position (\nameref{S1_Fig} and \nameref{S1_Fig}).

@@

Our printed pipette improves on existing open design pipettes in several ways. 
Most significantly the user is able to adjust the syringe accurately without verifying the volume with a scale.
The pipette can be adjusted to any discrete volume within range.
In addition, the assembly requires no permanent connections using tape or glue which allows for re-configuration and easy replacement of parts.
Conveniently, our design can also reach to the bottom of a 15 mL conical tube allowing tasks such as aspirating supernatant fluid from a cell pellet.
Unlike existing designs our design does not use a membrane that may wear out and require replacement.
The only major limitation of this design compared to the biropipette is the option for a pipette tip ejector.
The biropipette also uses arguably easier to source parts (a pen VS a syringe) relative to what is required from our design.
The biropipette also was developed in OpenSCAD which is free and open source CAD software where our design was created in Solidworks a proprietary software.

>>>>

Our solution was to replace the built-in scale with a scale that accounted for the expansion.
We compared expected volumes with actual measurements and noticed a linear relationship.
We scaled up the graduations by a factor of 1.027x for both the 100-1000 $\mu$L, and 30-300 $\mu$L configurations.
These scales were exported to portable document format (PDF) so that they are most easily printed to scale.
These adjusted scales are printed on paper or a transparency sheet and taped onto the syringe with the zero at plunger in the latched position (\nameref{S1_Fig} and \nameref{S1_Fig}).

@@

Our printed pipette improves on existing open design pipettes in several ways. 
Most significantly the user is able to adjust the syringe accurately without verifying the volume with a scale.
The pipette can be adjusted to any discrete volume within range.
In addition, the assembly requires no permanent connections using tape or glue which allows for re-configuration and easy replacement of parts.
Conveniently, our design can also reach to the bottom of a 15 mL conical tube allowing tasks such as aspirating supernatant fluid from a cell pellet.
Unlike existing designs our design does not use a membrane that may wear out and require replacement.
The only major limitation of this design compared to the biropipette is the option for a pipette tip ejector.
The biropipette also uses arguably easier to source parts (a pen VS a syringe) relative to what is required from our design.
The biropipette also was developed in OpenSCAD which is free and open source CAD software where our design was created in Solidworks a proprietary software.
This creates a limitation for users who may not have access to the proprietary software used to make the design.
Fortunately the produced STL files are universal and can be imported an modified by any CAD software.

The luer to pipette tip connection is a good candidate for a 3D printed solution.
Unfortunately the current state of FDM can not make this adapter with high enough resolution or critically, surface smoothness.
Other printing techniques, such as stereolithography (SLA) and MultiJet Printing (MJP), provide higher resolution and smoother finishing, yet FDM is the the most widely available and affordable of printing technologies.
SLA printers are coming down in price but are still significantly more expensive especially considering the higher cost of the consumable resin vs. FDM filament.
Ultimately the goal of this project is to make this pipette cheap and easy to make.
